Supplementary Information

### 2020-08-28 doc/manuscript/MEE_manuscript_SI.Rmd
knit in table
#73

This will include:

site | species | n trees (all) | n cores (all) | n trees (DBH) | n cores (DBH) | DBH range: sampled | DBH range: reconstructed | date range | collected by
-- | -- | -- | -- | -- | -- | -- | -- | -- | --

>>>>

```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
ss_table <- read.csv("tables_figures/sampling_details.csv", stringsAsFactors = FALSE, check.names = FALSE)
kable(ss_table, format = "latex", booktabs = TRUE,   escape = F, linesep = c('\\addlinespace'))%>%
  row_spec(0, italic = F, bold = T) %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), protect_latex = T) 
```
